Key Provisioning for Internet of Things via Light

### 2015-09-10 paper/paper.tex
change abstract: keys could be generated on mote, but how do they get to others in a secure way?

\begin{abstract}
The rise of the Internet of Things (IoT) is associated with an enourmous increase in every-day devices that get connected to the Internet.
In order to avoid privacy issues and security threats those devices have to communicate securely using state-of-the-art encryption techniques.
The initial keying material needed for this cannot be created on those devices itself due to memory and power constraints.
We propose a secure method for IoT-device initialization by transmitting initial keying material via light.
The transmission can be executed using an off-the-shelf smart phone and doesn't require any technical expertise.
\end{abstract}

>>>>

\begin{abstract}
The rise of the Internet of Things (IoT) is associated with an enormous increase in every-day devices that get connected to the Internet.
In order to avoid privacy issues and security threats those devices have to communicate securely using state-of-the-art encryption techniques.
However, these techniques often rely on predistributed keying material.
Secure distribution of these initial keys \textit{before} securing techniques are operational remains a major problem.

We propose a secure method for IoT-device initialization by transmitting initial keying material via light.
The transmission can be executed using an off-the-shelf smart phone and doesn't require any technical expertise.
\end{abstract}
